---
output:
  html_document:
    keep_md: yes
    fig.width: 5
    fig.height: 3
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/Lock5withR)](http://cran.r-project.org/package=Lock5withR)
[![Travis-CI Build Status](https://travis-ci.org/rpruim/Lock5withR.svg?branch=master)](https://travis-ci.org/rpruim/Lock5withR)

Lock5withR
==========

This R Companion to 
[Statistics: Unlocking the Power of Data](http://lock5stat.com/)
by Lock, Lock, Lock, Lock, and Lock provides

 * a companion text 
 * an R package (`Lock5withR`)

## Companion Text

 * *Lock5 with R*, a companion to *Statistics: Unlocking the Power of Data* 
 is available 
 [as a PDF](https://github.com/rpruim/Lock5withR/blob/master/Book/Lock5withR.pdf) 
 * The authors are Randall Pruim and Lana Park.  
 
## R Package

The `Lock5withR` package can be installed from github using

```{r eval=FALSE}
devtools::install_github("rpruim/Lock5withR")
```

This package contains all of the data sets used in the package and the `locket()` function which can be used to run any of 
`r length(Lock5withR::locket())` code chunks from the companion.  

For example:

```{r message=FALSE}
require(Lock5withR)
require(mosaic)
```
```{r}
locket("Example2.11")
```

### Relationship to `Lock5Data`

The Locks have created an R package called `Lock5Data` that contains the data sets from their text.
Some of these data sets have been modified in `Lock5withR` to make them easier to use with R.  Modified data sets include the following:

```
AllCountries    BikeCommute      BodyTemp50       CaffeineTaps 
CarbonDioxide   CO2              EmployedACS      Flight179 
GPAGender       ICUAdmissions    MiamiHeat        MindsetMatters 
NFLScores2011   NutritionStudy   RestaurantTips   RetailSales 
SalaryGender    SampCountries    SandP500         SleepStudy 
SpeedDating     StudentSurvey    USStates         WaterTaste 
Wetsuits
```
Typically changes involved the inclusion of additional variables with better encodings.  Somtimes 
variables are replaced.  In the case of `CO2` the data set has been renamed `AtmosphericCO2` to 
avoid a name collision with a data set in the `datasets` package.

The `locket()` function is only available in `Lock5withR`.
