---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

Lock5withR
==========

R Companion to 
[Statistics: Unlocking the Power of Data](http://lock5stat.com/)
by Lock, Lock, Lock, Lock, and Lock.

## Compantion Text

## R Package

The `Lock5withR` package can be installed from github using

```{r eval=FALSE}
devtools::install_github("rpruim/Lock5withR")
```

This package contains all of the data sets used in the package and the `locket()` function which 
can be used to run any code chunk from the campanion.  For example:

```{r message=FALSE}
require(Lock5withR)
require(mosaic)
```
```{r}
locket("Example2.11")
```

### Relationship to `Lock5Data`

The Locks have created an R package called `Lock5Data` that contains the data sets from their text.
Some of these data sets have been modified in `Lock5withR` to make them easier to use with R.  Modified data sets include the following:

```
AllCountries       BikeCommute         BodyTemp50          CaffeineTaps 
CarbonDioxide      CO2                 EmployedACS         Flight179 
GPAGender          ICUAdmissions       MiamiHeat           MindsetMatters 
NFLScores2011      NutritionStudy      RestaurantTips      RetailSales 
SalaryGender       SampCountries       SandP500            SleepStudy 
SpeedDating        StudentSurvey       USStates            WaterTaste 
Wetsuits
```
Typically changes involved the inclusion of additional variables with better encodings.  Somtimes 
variables are replaced.  In the case of `CO2` the data set has been renamed `AtmosphericCO2` to 
avoid a name collision with a data set in the `datasets` package.
